Glucose ingestion before and after resistance training does not augment ribosome biogenesis in healthy moderately trained young adults

### 2023-04-26 ribose-paper.postfeedback.RMD
abstract

*Introduction:*Responses to resistance training (RT) are not uniform across the population, and individuals responding poorly to RT show a blunted ability to produce novel ribosomes [@hammarstrom2020;@stec2016]. Recent research solidifies the relationship between increased rates of total RNA and the magnitude of RT-induced adaptations [@hammarstrom2020;@hammarstrom2022@figueiredo2019rev], with ribosome abundance being associated with UBF protein levels [@hammarstrom2022]. However, 10-15% of individuals undertaking a period of RT showed considerable impaired growth [@alvarez2018;@mann2014;@thalacker2013]. Since modifying RT alone does not convert low-responders to high-responders [@hammarstrom2020] other means than RT per se is necessary to circumvent this discrepancy. High glucose treatment has been observed to augment rDNA transcription in vitro[@tanaka2018], however, its effect on RT-induced adaptations remains quite unexplored.  
*Methods:*Sixteen healthy moderately trained participants were included and randomized to unilateral resistance training with glucose- and placebo supplement. Participants remained fasted overnight receiving glucose/placebo and protein only before and after RT. Resistance training consisted of 3 sets of 10 repetitions maximum unilateral leg press and knee extension. Micro biopsies were sampled pre (T1/T2) and post (T3/T4) the intervention, and maximal unilateral isometric and isokinetic knee extension torque were measured pre (T0), during (days 4, 5, 8, 9) and post (T3/T4, day 13) the intervention.  
*Results:*Despite robust increases in total RNA and rRNA in glucose and placebo (RNA: 26 and 22% respectively, rRNA: 33-43% and 33-41% respectively), there were no differences between supplements (p > 0.05). Content of c-Myc increased 42% more (*p* = 0.027) in placebo compared to glucose, but there were no differences in content of UBF (*p* = 0.185) and rpS6 (*p* = 0.178) between treatments. Further, there was a linear relationship between content of UBF and total RNA, where an increase of 1 SD unit in UBF equated to 13% increase in total RNA (*p* = 0.002). Lastly, there were no differences between supplements in maximal unilateral isometric knee extension force and isokinetic peak torque during the intervention (p > 0.05) and following the last session (p > 0.05), apart from the 60 d/s test before last RT session (p < 0.05). 
*Conclusion:* Glucose supplement before and after RT does not acutely augment ribosome biogenesis, nor does it enhance muscular performance and recovery after two weeks of heavy RT in moderately trained young individuals.

>>>>

*Introduction:*Responses to resistance training (RT) are not uniform across the population, and individuals responding poorly to RT show a blunted ability to produce novel ribosomes [@hammarstrom_benefits_2020; @stec_ribosome_2016]. Recent research solidifies the relationship between increased rates of total RNA and the magnitude of RT-induced adaptations [@hammarstrom_benefits_2020; @hammarstrom_ribosome_2022; @figueiredo_revisiting_2019], with ribosome abundance being associated with UBF protein levels [@hammarstrom_ribosome_2022]. However, 10-15% of individuals undertaking a period of RT showed considerable impaired growth [@alvarez_interindividual_2018; @mann_high_2014; @thalacker-mercer_cluster_2013]. Since modifying RT alone does not convert low-responders to high-responders [@hammarstrom_benefits_2020] other means than RT per se is necessary to circumvent this discrepancy. High glucose treatment has been observed to augment rDNA transcription in vitro[@sebata_control_2018], however, its effect on RT-induced adaptations remains quite unexplored.  
*Methods:*Sixteen healthy moderately trained participants were included and randomized to unilateral resistance training with glucose- and placebo supplement. Participants remained fasted overnight receiving glucose/placebo and protein only before and after RT. Resistance training consisted of 3 sets of 10 repetitions maximum unilateral leg press and knee extension. Micro biopsies were sampled pre (T1/T2) and post (T3/T4) the intervention, and maximal unilateral isometric and isokinetic knee extension torque were measured pre (T0), during (days 4, 5, 8, 9) and post (T3/T4, day 13) the intervention.  
*Results:*Despite robust increases in total RNA and rRNA in glucose and placebo (RNA: 26 and 22% respectively, rRNA: 33-43% and 33-41% respectively), there were no differences between supplements (p > 0.05). Content of c-Myc increased 42% more (*p* = 0.027) in placebo compared to glucose, but there were no differences in content of UBF (*p* = 0.185) and rpS6 (*p* = 0.178) between treatments. Further, there was a linear relationship between content of UBF and total RNA, where an increase of 1 SD unit in UBF equated to 13% increase in total RNA (*p* = 0.002). Lastly, there were no differences between supplements in maximal unilateral isometric knee extension force and isokinetic peak torque during the intervention (p > 0.05) and following the last session (p > 0.05), apart from the 60 d/s test before last RT session (p < 0.05). 
*Conclusion:* Glucose supplement before and after RT does not acutely augment ribosome biogenesis, nor does it enhance muscular performance and recovery after two weeks of heavy RT in moderately trained young individuals.
